---
output:
  html_document: default
  html_notebook: default
---
```{r}
#introducir base de datos
library(readxl)
CPI2019 <- read_excel("D:/Users/Giancarlo/Desktop/2020-2/Estadistica2/2019_CPI_FULLDATA/2019_CPI_FULLDATA/CPI2019.xlsx")
View(CPI2019)
```

```{r}
names(CPI2019)
```
```{r}
#limpieza de datos
#cambio de nombre de columnas  y eliminacion de las sobrantes
CPI2019$pais=CPI2019$Country
CPI2019$Country=NULL
```
```{r}
CPI2019$Score=CPI2019$`CPI score 2019`
CPI2019$`CPI score 2019`=NULL
```
```{r}
CPI2019[,c(1:16)]=NULL

```
```{r}
CPI2019[,c(1:4)]=NULL

```
```{r}
#Conversión de Score a variable numérica
CPI2019$Score=as.numeric(CPI2019$Score)

```
```{r}
#revisar los cambios realizados
str(CPI2019)
```
```{r}
#Comandos para ver la data y tener una idea general de los valores
table(CPI2019$Score)
summary(CPI2019$Score)
```
```{r}
#cambio de nombre de la base de datos
CPImodificado=CPI2019

```
```{r,echo=FALSE}
str(CPImodificado)
```
```{r}
#información general de la nueva base de datos
names(CPImodificado)
```
```{r}
#verificar NA's
CPImodificado[!complete.cases(CPImodificado),]

```
```{r}
#exportar base de datos
setwd("D:/Users/Giancarlo/Desktop/2020-2")
write.table(CPImodificado, file="CPIDATAfinal.csv",sep=";",row.names = F)
```

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
